---
title: "Assignment 5"
author: "Maggie Hsu"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

set.seed(8105) #set seed
```
Suppose you put n people in a room, and want to know the probability that at least two people share a birthday. For simplicity, we’ll assume there are no leap years (i.e. there are only 365 days) and that birthdays are uniformly distributed over the year (which is actually not the case).

Write a function that, for a fixed group size, randomly draws “birthdays” for each person; checks whether there are duplicate birthdays in the group; and returns TRUE or FALSE based on the result.
```{r problem 1 - function}
#Let integers 1-365 represent dates from January 1st to December 31st (no leap days)
b_days <- function(n) { #where n is the number of people in the group
  birthdays <- sample(1:365,n,replace = TRUE)
  result = (sum(duplicated(birthdays)) > 0) 
  result
} 
```


Next, run this function 10000 times for each group size between 2 and 50. For each group size, compute the probability that at least two people in the group will share a birthday by averaging across the 10000 simulation runs. 

```{r problem 1 - group simulation}

```

Make a plot showing the probability as a function of group size, and comment on your results.
```{r problem 1 - plot}

```


```{r problem 2}
#Initialize elements
n = 30
mu = 0
sigma = 5

datasets <- x = rnorm(n, mean = mu, sd = sigma)



```

```{r problem 3}

```